---
title: "Masterthesis script"
author: "Aline Laura Metzler"
date: "5/26/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


wefqwef
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
```

# Masterarbeit Script
 

## Deskriptive Analysis

Data is read and prepared in separate file. The variable for the type of voter is created by filtering individuals that lived in the same community for at least ten consecutive votes. For each individeual the 10 most recent votes were selected. This allows for the classification of these individuals into "never voters" (0-1 participation), "selective voters" (2-8 participation) and "always voters" (9-10 participation). 

```{r}
source("MA_adminDataPreparation.R", local = knitr::knit_global())
```

### Make categories for numerical variables

Age:
1st Quintile: 18-30 years
2nd Quintile: 31-45 years
3rd Quintile: 46-60 years
4th Quintile: 61-75 years
5th Quintile: >75 years

Gender:
Male: 1
Female: 2

(Zivilstand: )

Konfession:
- Christliche Konfession
- Andere/Keine Konfession

Aufenthalt in Gemeinde:
- 0-10: Jahre
- >10 Jahre

Zugezogen:
- In CH Geboren
- Zugezogen 

Einkommen (massgebendes Einkommen vs. Äquivalnezeinkommen:
1st Quartile: 0-25'000.-
2nd Quartile: 25'000-55'000.-
3rd Quartile: 55'000-90'000.-
4th Quartile: >90'000.-

Vermögen:
1st Quartile: 0-8'000.-
2nd Quartile: 8'000-60'000.-
3rd Quartile: 60'000-185'000.-
4th Quartile: >185'000.-

```{r}

data_mlogit <- data_mlogit %>% 
  mutate(alter_c = case_when(
    alter_v <= 30 ~ "18-30-Jährige",
    alter_v > 30 && alter_v <= 45 ~ "31-45-Jährige",
    alter_v > 45 && alter_v <= 60  ~ "46-60-Jährige",
    alter_v > 60 && alter_v <= 75 ~ "61-75-Jährige",
    alter_v > 75 ~ "Über 75-Jährige"
    )) %>% 
  mutate(sex_c = case_when(
    sex == 1 ~ "Mann",
    sex == 2 ~ "Frau"
  )) %>% 
  mutate(konfession_c = case_when(
    konfession %in% c(1, 2) ~ "Christliche Konfession",
    TRUE ~ "Andere/keine Konfession"
  )) %>% 
  mutate(residenz10 = case_when(
    aufenthaltsdaueringemeinde %in% c(1, 2, 3) ~ "0-10 Jahre",
    TRUE ~ "Mehr als 10 Jahre"
  )) %>% 
  mutate(zugezogen = case_when(
    Geburtsstaat == 8100 ~ "In CH geboren",
    TRUE ~ "Zugezogen"
  )) %>% 
  mutate(mEinkommen_c = case_when(
    massgebendesEinkommen <= 25000 ~ "0-25'000.-",
    massgebendesEinkommen > 25000 && massgebendesEinkommen <= 55000 ~ "25'000-55'000.-",
    massgebendesEinkommen > 55000 && massgebendesEinkommen <= 90000 ~ "55'000-90'000.-",
    massgebendesEinkommen > 90000 ~ "Über 90'000.-"
  )) %>% 
  mutate(Vermoegen_c = case_when(
    reinvermoegen <= 8000 ~ "0-8'000.-",
    reinvermoegen > 8000 && reinvermoegen <= 60000 ~ "8'000-60'000.-",
    reinvermoegen > 60000 && reinvermoegen <= 185000 ~ "60'000-185'000.-",
    reinvermoegen > 185000 ~ "Über 185'000.-"
  ))
  


```


```{r}

data %>% 
  group_by(abstimmungsjahr) %>% 
  count(is.na(steuerb_einkommen))


p1 <- data %>% 
  group_by(abstimmungsjahr, bfsnr) %>% 
  count(is.na(reinvermoegen)) %>% 
  rename(`NA Steuerdaten` = `is.na(reinvermoegen)`) %>% 
  #mutate(abstimmungsjahr = as.year(abstimmungsjahr)) %>% 
  mutate(bfsnr = case_when(
    bfsnr == 3203 ~ "Stadt St. Gallen",
    bfsnr == 3231 ~ "Au (SG)",
    bfsnr == 3237 ~ "Thal",
    bfsnr == 3293 ~ "Mels",
    bfsnr == 3295 ~ "Quarten",
    bfsnr == 3338 ~ "Schmerikon",
    bfsnr == 3359 ~ "Wildhaus-Alt St.Johann",
    bfsnr == 3408 ~ "Uzwil",
    bfsnr == 3443 ~ "Gossau (SG)"
  )) %>% 
  ggplot(aes(x=abstimmungsjahr, y=n, group=`NA Steuerdaten`, color=`NA Steuerdaten`)) +
  geom_line() +
  facet_wrap(~ bfsnr, ncol = 3) +
  scale_x_date(date_breaks = "1 year",date_labels = "%Y") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p1

```

